The Shape Matching Element Method for Meshless Animation of NURBs Models

### 2021-01-24 paper/sections/methods.tex
added network flow figure

\begin{algorithm}[h]
    \label{alg:sem}
	\caption{Shape Matching Element Algorithm}\label{sem_algorithm}
	\begin{algorithmic}[1]
		\Procedure{Preprocess}{$model$}
		\State{// Get initial DOF and sample boundary}
		\State $\mathbf{q^0} \gets \text{GetControlPoints}(model)$ \Comment{Section 4}
		\State $\mathbf{J}, \mathbf{W} \gets \text{SampleNURBS}(model)$ \Comment{Section 4}
		\State $\mathbf{x^0} \gets \mathbf{Jq^0}$
		\State{$\mathbf{q} \gets \mathbf{q^0}$}
      \Statex

@@

From the set of blending weights we seek to construct a set of candidate deformation origins and then produce a set of deformation origins, $\XBs$, adhering to the outlined requirements. These requirements admit a graph structure, which we exploit by forming a simple network flow problem that produces a solution satisfying the requirements. The pairwise relationships between parts and deformation origins can be realized as a bipartite network flow problem. Flow between a part and origin is constrained to binary values and a flow value on edge between a part and origin candidate indicate that the part is paired with this deformation origin. We organize the problem so that the source node is connected to each candidate origin node, and the sink node is connected with each part. We place a capacity constraint of $1$ on the sink's edge, which enforces the constraint that each part is paired with one origin.

>>>>

\ty{Update notation, split this into two figures}
\begin{algorithm}[h]
    \label{alg:sem}
	\caption{Shape Matching Element Algorithm}\label{sem_algorithm}
	\begin{algorithmic}[1]
		\Procedure{Preprocess}{$model$}
		\State{// Get initial DOF and sample boundary}
		\State $\mathbf{q^0} \gets \text{GetControlPoints}(model)$ \Comment{Section 4}
		\State $\mathbf{J}, \mathbf{W} \gets \text{SampleNURBS}(model)$ \Comment{Section 4}
		\State $\mathbf{x^0} \gets \mathbf{Jq^0}$
		\State{$\mathbf{q} \gets \mathbf{q^0}$}
      \Statex

@@

\begin{figure}[h]
    \includegraphics[width=\columnwidth]{figures/origin_network}
    \caption{Example structure for the network flow selection of deformation origins with an example shape on the right. Red arrows indicate each parts origin association.}
    \label{fig:multiparts}
\end{figure}

From the set of blending weights we seek to construct a set of candidate deformation origins and then produce a set of deformation origins, $\XBs$, adhering to the outlined requirements. These requirements admit a graph structure ~(\reffig{multiparts}), which we exploit by forming a simple network flow problem that produces a solution satisfying the requirements. The pairwise relationships between parts and deformation origins can be realized as a bipartite network flow problem. Flow between a part and origin is constrained to binary values and a flow value on edge between a part and origin candidate indicate that the part is paired with this deformation origin. We organize the problem so that the source node is connected to each candidate origin node, and the sink node is connected with each part. We place a capacity constraint of $1$ on the sink's edge, which enforces the constraint that each part is paired with one origin.
